Numerical simulations of the Cordilleran ice sheet through the last glacial cycle

### 2016-01-21 cordillera-cycle.tex
Rev. Jarosch: add references.

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

>>>>

\bibitem[{Clarke et~al.(2013)Clarke, Anslow, Jarosch, Radi{\'{c}}, Menounos, Bolch, and Berthier}]{Clarke.etal.2013}
Clarke, G. K.~C., Anslow, F.~S., Jarosch, A.~H., Radi{\'{c}}, V., Menounos, B., Bolch, T., and Berthier, E.: Ice Volume and Subglacial Topography for Western Canadian Glaciers from Mass Balance Fields, Thinning Rates, and a Bed Stress Model, J. Climate, 26, 4282--4303,
doi:\href{http://dx.doi.org/10.1175/jcli-d-12-00513.1}{10.1175/jcli-d-12-00513.1}, 2013.

@@

\bibitem[{Cuffey and Paterson(2010)}]{Cuffey.Paterson.2010}
Cuffey, K.~M. and Paterson, W. S.~B.: The physics of glaciers, Elsevier, Amsterdam, 2010.

@@

\bibitem[{Glen(1952)}]{Glen.1952}
Glen, J.: Experiments on the deformation of ice, J. Glaciol., 2, 111--114, 1952.

@@

\bibitem[{Greve(1997)}]{Greve.1997}
Greve, R.: A continuum-mechanical formulation for shallow polythermal ice sheets, Philos. T. R. Soc. A, 355, 921--974,
doi:\href{http://dx.doi.org/10.1098/rsta.1997.0050}{10.1098/rsta.1997.0050}, 1997.

@@

\bibitem[{Hijmans et~al.(2005)Hijmans, Cameron, Parra, Jones, and Jarvis}]{Hijmans.etal.2005}
Hijmans, R.~J., Cameron, S.~E., Parra, J.~L., Jones, P.~G., and Jarvis, A.: Very high resolution interpolated climate surfaces for global land areas, Int. J. Climatol., 25, 1965--1978,
doi:\href{http://dx.doi.org/10.1002/joc.1276}{10.1002/joc.1276}, 2005.

@@

\bibitem[{Jarosch et~al.(2012)Jarosch, Anslow, and Clarke}]{Jarosch.etal.2012}
Jarosch, A.~H., Anslow, F.~S., and Clarke, G. K.~C.: High-resolution precipitation and temperature downscaling for glacier models, Clim. Dynam., 38, 391--409,
doi:\href{http://dx.doi.org/10.1007/s00382-010-0949-1}{10.1007/s00382-010-0949-1}, 2012.

@@

\bibitem[{Lliboutry and Duval(1985)}]{Lliboutry.Duval.1985}
Lliboutry, L.~A. and Duval, P.: Various isotropic and anisotropic ices found in glaciers and polar ice caps and their corresponding rheologies, Ann. Geophys., 3, 207--224, 1985.

@@

\bibitem[{L{\"u}thi et~al.(2002)L{\"u}thi, Funk, Iken, Gogineni, and Truffer}]{Luthi.etal.2002}
L{\"u}thi, M., Funk, M., Iken, A., Gogineni, S., and Truffer, M.: Mechanisms of fast flow in {J}akobshavns {I}sbr{\ae}, {G}reenland; {P}art {III}: measurements of ice deformation, temperature and cross-borehole conductivity in boreholes to the bedrock, J. Glaciol., 48, 369--385,
doi:\href{http://dx.doi.org/10.3189/172756502781831322}{10.3189/172756502781831322}, 2002.

@@

\bibitem[{Nye(1953)}]{Nye.1953}
Nye, J.~F.: The Flow Law of Ice from Measurements in Glacier Tunnels, Laboratory Experiments and the Jungfraufirn Borehole Experiment, Proc. R. Soc. London, Ser. A, 219, 477--489, 1953.

@@

\bibitem[{Paterson and Budd(1982)}]{Paterson.Budd.1982}
Paterson, W. S.~B. and Budd, W.~F.: Flow parameters for ice sheet modeling, Cold Reg. Sci. Technol., 6, 175--177, 1982.

@@

\bibitem[{Rignot et~al.(2013)Rignot, Mouginot, Larsen, Gim, and Kirchner}]{Rignot.etal.2013}
Rignot, E., Mouginot, J., Larsen, C.~F., Gim, Y., and Kirchner, D.: Low-frequency radar sounding of temperate ice masses in Southern Alaska, Geophys. Res. Lett., 40, 5399--5405,
doi:\href{http://dx.doi.org/10.1002/2013gl057452}{10.1002/2013gl057452}, 2013.
